### 2023-12-26 sections/4-results.tex
changes to results; new figure label

Figures~\ref{fig:results:fashion-mnist-scaling}, ~\ref{fig:results:glove-25-scaling}, and ~\ref{fig:results:sift-scaling} show the scaling behavior of CAKES algorithms and existing algorithms on augmented versions of the following ann-benchmark datasets: fashion-mnist under Euclidean distance, glove-25 under cosine distance, and sift under Euclidean distance.
Figure~\ref{fig:results:random-scaling} shows the scaling behavior of CAKES algorithms and existing algorithms on a completely randomly generated dataset with same cardinality and dimensionality as sift (1 million points in 128 dimensions).
Figures~\ref{fig:results:silva-scaling} and ~\ref{fig:results:radioml-scaling} show the scaling behavior of CAKES on Silva and RadioML respectively.
The horizontal axis in each figure shows the cardinality of the augmented dataset with synthetic points (see Section \ref{subsec:methods:synthetic-data}).
The left-most point on each line is on the original dataset without any synthetic augmentation.
The vertical axis denotes throughput in queries per second.
Both axes are on a logarithmic scale.
In this section, we report results only for $k$-NN search with $k = 10$, but similar plots for $k=100$ can be found in the Supplement.
{\color{red} TODO: revisit this sentence with cosine dist plot in mind: In these plots, we label the recall for algorithms which do not exhibit perfect recall; if no such labels are given for an algorithm, then that algorithm exhibits perfect recall" }.

@@

In Figure~\ref{fig:results:fashion-mnist-scaling}, which shows results for Fashion-mnist, we observe that as cardinality increases, the CAKES algorithms (GreedySieve in blue, Repeated $\rho$-NN in green, and Sieve in red) exhibit higher throughput than na\"{i}ve linear search (plotted in orange).
In particular, we see that GreedySieve and Sieve begin to exhibit sublinear time performance at a cardinality near $10^5$ (i.e., at a multiplier of about {\color{red} add value} times the original dataset's cardinality). 
We also observe that CAKES's algorithms outperform FAISS-IVF (plotted in pink) for all cardinalities larger than the original dataset's cardinality.
Though state-of-the-art algorithms HNSW (plotted in gray), and Annoy (plotted in purple) have higher throughput than CAKES for all cardinalities, we note that CAKES always exhibits perfect recall while HNSW and Annoy exhibit much lower recall, as shown in Table~\ref{table:results:ann-fashion}.
For example, at a multiplier as low as eight, HNSW and ANNOY have recall of 0.525 and 0.857 respectively,
and this recall gets worse as the multiplier increases.
Meanwhile, CAKES exhibits perfect recall.
Amongst the CAKES algorithms, GreedySieve consistently performs best on this dataset, exhibiting sublinear time performance with increasing multipliers.

With glove-25 (Figure~\ref{fig:results:glove-25-scaling}), we observe that each of CAKES' algorithms outperforms linear search at some cardinality.
Specifically, all three of CAKES' algorithms outperform linear search at a cardinality just slightly more than the original dataset's cardinality, $10^6$.
Similar to the results for Fashion-mnist, we see that CAKES's algorithms outperform FAISS-IVF for all cardinalities greater than $10^7$.
We see once again that HNSW and Annoy have higher throughput than CAKES's algorithms for all cardinality multipliers, CAKES's algorithms exhibit better recall at all multipliers, as shown in Table~\ref{table:results:ann-glove-25}.
In particular, at a multiplier as low as two, HNSW and ANNOY have recall as low as 0.607 and 0.832 respectively, and this recall continues to decrease as we increase the multiplier.
In contrast, CAKES exhibits perfect recall at all multipliers.
On this dataset, unlike with fashion-mnist, Repeated $\rho$-NN, plotted in green, is consistently the best-performing CAKES algorithm.

In Figure~\ref{fig:results:sift-scaling}, which displays the scaling behavior of algorithms on the Sift dataset, we observe that while linear search performs best for lower cardinalities, our algorithms begin to outperform our implementation of linear search and FAISS-IVF at a cardinality near $10^7$.
For this dataset, Sieve, plotted in red, is the highest-throughput CAKES algorithm for all cardinalities.
Similar to the results with Fashion-mnist and Glove-25, we observe that while HNSW and Annoy exhibit higher throughput than CAKES's algorithms for all cardinality multipliers, CAKES has better recall.
Table~\ref{table:results:ann-sift} shows that even with a multiplier of 1 (i.e., the original dataset), HNSW and Annoy have recall as low as 0.782 and 0.686 respectively, while CAKES exhibits perfect recall.

@@

{\color{red} TODO: Add Silva and RadioML results.}

@@

\caption{Algorithm performance across six datasets, including a randomly-generated dataset. In each plot, the horizontal axis represents increasing cardinality (size) of the dataset, while the vertical axis represents the throughput in queries per second (higher is better). TODO say something about plots that didn't finish.}
\end{figure}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{fashion-mnist} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 1.33~$\times10^{4}$ & 0.954 & 2.19~$\times10^{3}$ & 0.950 & 2.13~$\times10^{2}$  & 1.000 & 2.01~$\times10^{3}$ & 1.000* & 2.17~$\times10^{3}$ & 1.000 \\
                    \hline
                    2   & 1.38~$\times10^{4}$ & 0.803 & 2.12~$\times10^{3}$ & 0.927 & 1.06~$\times10^{2}$  & 1.000 & 9.39~$\times10^{2}$ & 1.000* & 1.14~$\times10^{3}$ & 1.000 \\
                    \hline
                    4   & 1.66~$\times10^{4}$ & 0.681 & 2.04~$\times10^{3}$ & 0.898 & 5.31~$\times10^{1}$  & 1.000 & 4.61~$\times10^{2}$ & 0.997  & 9.82~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 1.68~$\times10^{4}$ & 0.525 & 1.93~$\times10^{3}$ & 0.857 & 2.66~$\times10^{1}$  & 1.000 & 2.26~$\times10^{2}$ & 0.995  & 1.18~$\times10^{3}$ & 1.000 \\
                    \hline
                    16  & 1.87~$\times10^{4}$ & 0.494 & 1.84~$\times10^{3}$ & 0.862 & 1.33~$\times10^{1}$  & 1.000 & 1.17~$\times10^{2}$ & 0.991  & 1.20~$\times10^{3}$ & 1.000 \\
                    \hline
                    32  & 1.56~$\times10^{4}$ & 0.542 & 1.85~$\times10^{3}$ & 0.775 & 6.65~$\times10^{0}$  & 1.000 & 5.91~$\times10^{1}$ & 0.985  & 1.16~$\times10^{3}$ & 1.000 \\
                    \hline
                    64  & 1.50~$\times10^{4}$ & 0.378 & 1.78~$\times10^{3}$ & 0.677 & 3.32~$\times10^{0}$  & 1.000 & 2.61~$\times10^{1}$ & 0.968  & 1.10~$\times10^{3}$ & 1.000 \\
                    \hline
                    128 & 1.49~$\times10^{4}$ & 0.357 & 1.66~$\times10^{3}$ & 0.538 & 1.66~$\times10^{0}$  & 1.000 & 1.33~$\times10^{1}$ & 0.964  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                    256 & --                  & --    & 1.60~$\times10^{3}$ & 0.592 & 8.31~$\times10^{-1}$ & 1.000 & 6.65~$\times10^{0}$ & 0.962  & 1.06~$\times10^{3}$ & 1.000 \\
                    \hline
                    512 & --                  & --    & 1.83~$\times10^{3}$ & 0.581 & 4.16~$\times10^{-1}$ & 1.000 & 3.56~$\times10^{0}$ & 0.949  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{glove-25} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{table:results:ann-glove-25}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 2.28~$\times10^{4}$ & 0.801 & 2.83~$\times10^{3}$ & 0.835 & 2.78~$\times10^{2}$ & 1.000 & 2.38~$\times10^{3}$ & 1.000* & 7.22~$\times10^{2}$ & 1.000* \\
                    \hline
                    2   & 2.38~$\times10^{4}$ & 0.607 & 2.70~$\times10^{3}$ & 0.832 & 1.39~$\times10^{2}$ & 1.000 & 1.19~$\times10^{3}$ & 1.000* & 5.75~$\times10^{2}$ & 1.000* \\
                    \hline
                    4   & 2.50~$\times10^{4}$ & 0.443 & 2.61~$\times10^{3}$ & 0.839 & 6.98~$\times10^{1}$ & 1.000 & 6.19~$\times10^{2}$ & 1.000* & 6.25~$\times10^{2}$ & 1.000* \\
                    \hline
                    8   & 2.78~$\times10^{4}$ & 0.294 & 2.51~$\times10^{3}$ & 0.834 & 3.49~$\times10^{1}$ & 1.000 & 3.03~$\times10^{2}$ & 1.000* & 5.93~$\times10^{2}$ & 1.000* \\
                    \hline
                    16  & 3.11~$\times10^{4}$ & 0.213 & 2.23~$\times10^{3}$ & 0.885 & 1.74~$\times10^{1}$ & 1.000 & 1.51~$\times10^{2}$ & 1.000* & 5.49~$\times10^{2}$ & 1.000* \\
                    \hline
                    32  & 3.24~$\times10^{4}$ & 0.178 & 2.01~$\times10^{3}$ & 0.764 & 8.70~$\times10^{0}$ & 1.000 & 7.40~$\times10^{1}$ & 0.999  & 4.75~$\times10^{2}$ & 1.000* \\
                    \hline
                    64  & --                  & --    & 1.99~$\times10^{3}$ & 0.631 & 4.36~$\times10^{0}$ & 1.000 & 3.77~$\times10^{1}$ & 0.997  & 4.61~$\times10^{2}$ & 1.000* \\
                    \hline
                    128 & --                  & --    & --                  & --    & 2.18~$\times10^{0}$ & 1.000 & 1.90~$\times10^{1}$ & 0.998  & 4.41~$\times10^{2}$ & 1.000* \\
                    \hline
                    256 & --                  & --    & --                  & --    & 1.07~$\times10^{0}$ & 1.000 & 9.47~$\times10^{0}$ & 0.998  & 4.23~$\times10^{2}$ & 1.000* \\
                    \hline
                    % 512 & -- & -- & -- & -- & 0.544 & 1.000 & 4.499 & 0.996 & 0.000 & 0.000 \\
                    % \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{sift} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{table:results:ann-sift}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Scale}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1   & 1.93~$\times10^{4}$ & 0.782 & 3.98~$\times10^{3}$ & 0.686 & 7.26~$\times10^{1}$  & 1.000 & 6.98~$\times10^{2}$ & 1.000* & 5.52~$\times10^{2}$ & 1.000 \\
                    \hline
                    2   & 2.03~$\times10^{4}$ & 0.552 & 3.80~$\times10^{3}$ & 0.614 & 3.62~$\times10^{1}$  & 1.000 & 3.30~$\times10^{2}$ & 1.000* & 2.66~$\times10^{2}$ & 1.000 \\
                    \hline
                    4   & 2.18~$\times10^{4}$ & 0.394 & 3.69~$\times10^{3}$ & 0.637 & 1.82~$\times10^{1}$  & 1.000 & 1.65~$\times10^{2}$ & 1.000* & 1.43~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 2.48~$\times10^{4}$ & 0.298 & 3.58~$\times10^{3}$ & 0.710 & 9.08~$\times10^{0}$  & 1.000 & 7.72~$\times10^{1}$ & 1.000* & 7.94~$\times10^{1}$ & 1.000 \\
                    \hline
                    16  & 2.68~$\times10^{4}$ & 0.210 & 3.50~$\times10^{3}$ & 0.690 & 4.54~$\times10^{0}$  & 1.000 & 3.98~$\times10^{1}$ & 1.000* & 8.12~$\times10^{1}$ & 1.000 \\
                    \hline
                    32  & 2.75~$\times10^{4}$ & 0.193 & 3.44~$\times10^{3}$ & 0.639 & 2.27~$\times10^{0}$  & 1.000 & 2.09~$\times10^{1}$ & 0.999  & 7.81~$\times10^{1}$ & 1.000 \\
                    \hline
                    64  & --                  & --    & 3.39~$\times10^{3}$ & 0.678 & 1.14~$\times10^{0}$  & 1.000 & 8.87~$\times10^{0}$ & 0.997  & 7.43~$\times10^{1}$ & 1.000 \\
                    \hline
                    128 & --                  & --    & 3.36~$\times10^{3}$ & 0.643 & 5.66~$\times10^{-1}$ & 1.000 & 4.78~$\times10^{0}$ & 0.993  & 6.80~$\times10^{1}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

>>>>

Figures~\ref{fig:results:fashion-mnist-scaling}, ~\ref{fig:results:glove-25-scaling}, and ~\ref{fig:results:sift-scaling} show the scaling behavior of CAKES algorithms and existing algorithms on augmented versions of the following ann-benchmark datasets: fashion-mnist under Euclidean distance, glove-25 under cosine distance, and sift under Euclidean distance.
Figure~\ref{fig:results:random-scaling} shows the scaling behavior of CAKES algorithms and existing algorithms on a completely randomly generated dataset with same cardinality and dimensionality as sift (1 million points in 128 dimensions).
Figures~\ref{fig:results:silva-scaling} and ~\ref{fig:results:radioml-scaling} show the scaling behavior of CAKES on Silva and RadioML respectively.
The horizontal axis in each figure shows the cardinality of the augmented dataset with synthetic points (see Section \ref{subsec:methods:synthetic-data}).
The left-most point on each line is on the original dataset without any synthetic augmentation.
The vertical axis denotes throughput in queries per second.
Both axes are on a logarithmic scale.
In this section, we report results only for $k$-NN search with $k = 10$, but similar plots for $k=100$ can be found in the Supplement.
For HNSW and Annoy, we report the recall for each measurement in the plots. For algorithms which exhibit recall greater than $0.9995$, we do not report the recall in the plots, but we do report it in the tables below.

@@

In Figure~\ref{fig:results:fashion-mnist-scaling}, which shows results for Fashion-mnist, we observe that as cardinality increases, the CAKES algorithms (GreedySieve in blue, Repeated $\rho$-NN in green, and Sieve in purple) exhibit higher throughput than na\"{i}ve linear search (plotted in orange).
In particular, we see that GreedySieve and Sieve begin to exhibit sublinear time performance at a cardinality near $10^5$ (i.e., at a multiplier of about {\color{red} add value} times the original dataset's cardinality). 
We also observe that CAKES's algorithms outperform FAISS-IVF (plotted in pink) for all cardinalities larger than the original dataset's cardinality.
Though state-of-the-art algorithms HNSW (plotted in gray), and Annoy (plotted in yellow) have higher throughput than CAKES for all cardinalities, we note that CAKES always exhibits perfect recall while HNSW and Annoy exhibit much lower recall, as shown in Table~\ref{table:results:ann-fashion}.
For example, at a multiplier as low as eight, HNSW and Annoy have recall of 0.525 and 0.857 respectively,
and this recall gets worse as the multiplier increases.
Meanwhile, CAKES exhibits perfect recall.
Amongst the CAKES algorithms, GreedySieve consistently performs best on this dataset, exhibiting sublinear time performance with increasing multipliers.

With glove-25 (Figure~\ref{fig:results:glove-25-scaling}), we observe that each of CAKES' algorithms outperforms linear search at some cardinality.
Specifically, all three of CAKES' algorithms outperform linear search at a cardinality just slightly more than the original dataset's cardinality, $10^6$.
Similar to the results for Fashion-mnist, we see that CAKES's algorithms outperform FAISS-IVF for all cardinalities greater than $10^7$.
We see once again that HNSW and Annoy have higher throughput than CAKES's algorithms for all cardinality multipliers, CAKES's algorithms exhibit better recall at all multipliers, as shown in Table~\ref{table:results:ann-glove-25}.
In particular, at a multiplier as low as two, HNSW and Annoy have recall as low as 0.607 and 0.832 respectively, and this recall continues to decrease as we increase the multiplier.
In contrast, CAKES exhibits perfect recall at all multipliers.
On this dataset, unlike with fashion-mnist, Repeated $\rho$-NN is consistently the best-performing CAKES algorithm.

In Figure~\ref{fig:results:sift-scaling}, which displays the scaling behavior of algorithms on the Sift dataset, we observe that while linear search performs best for lower cardinalities, our algorithms begin to outperform our implementation of linear search and FAISS-IVF at a cardinality near $10^7$.
For this dataset, Sieve, is the highest-throughput CAKES algorithm for all cardinalities.
Similar to the results with Fashion-mnist and Glove-25, we observe that while HNSW and Annoy exhibit higher throughput than CAKES's algorithms for all cardinality multipliers, CAKES has better recall.
Table~\ref{table:results:ann-sift} shows that even with a multiplier of 1 (i.e., the original dataset), HNSW and Annoy have recall as low as 0.782 and 0.686 respectively, while CAKES exhibits perfect recall.

@@

For Silva and RadioML, we benchmarked only CAKES's algorithms.
Due to the massive sizes of these datasets, we took random sub-samples of the dataset with lower cardinalities for our benchmarks, rather than augmented versions of the dataset.
With Silva, as shown in Figure~\ref{fig:results:silva-scaling}, we observe that for all algorithms, throughput seems to linearly decrease as cardinality increases, but that it seems to begin levelling off near cardinality $10^5$. Until cardinality near $10^4$, GreedySieve is the highest-throughput CAKES algorithm, but for cardinalities greater than that, Repeated $\rho$-NN is the highest-throughput CAKES algorithm.

For RadioML, as shown in Figure~\ref{fig:results:radioml-scaling}, we observe that throughput declines nearly linearly the CAKES algorithms exhibit nearly indistinguishable performance for all cardinalities.

@@

\caption{Algorithm performance across six datasets, including a randomly-generated dataset. In each plot, the horizontal axis represents increasing cardinality (size) of the dataset, while the vertical axis represents the throughput in queries per second (higher is better). For some algorithms, we were not able to take measurements for each cardinality because the index-building took too much memory. {\color{red} Explain this better and be more specific} }
\label{fig:results:scaling-plots}
\end{figure}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{fashion-mnist} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Multiplier}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 1.33~$\times10^{4}$ & 0.954 & 2.19~$\times10^{3}$ & 0.950 & 2.13~$\times10^{2}$  & 1.000 & 2.01~$\times10^{3}$ & 1.000* & 2.17~$\times10^{3}$ & 1.000 \\
                    \hline
                    2   & 1.38~$\times10^{4}$ & 0.803 & 2.12~$\times10^{3}$ & 0.927 & 1.06~$\times10^{2}$  & 1.000 & 9.39~$\times10^{2}$ & 1.000* & 1.14~$\times10^{3}$ & 1.000 \\
                    \hline
                    4   & 1.66~$\times10^{4}$ & 0.681 & 2.04~$\times10^{3}$ & 0.898 & 5.31~$\times10^{1}$  & 1.000 & 4.61~$\times10^{2}$ & 0.997  & 9.82~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 1.68~$\times10^{4}$ & 0.525 & 1.93~$\times10^{3}$ & 0.857 & 2.66~$\times10^{1}$  & 1.000 & 2.26~$\times10^{2}$ & 0.995  & 1.18~$\times10^{3}$ & 1.000 \\
                    \hline
                    16  & 1.87~$\times10^{4}$ & 0.494 & 1.84~$\times10^{3}$ & 0.862 & 1.33~$\times10^{1}$  & 1.000 & 1.17~$\times10^{2}$ & 0.991  & 1.20~$\times10^{3}$ & 1.000 \\
                    \hline
                    32  & 1.56~$\times10^{4}$ & 0.542 & 1.85~$\times10^{3}$ & 0.775 & 6.65~$\times10^{0}$  & 1.000 & 5.91~$\times10^{1}$ & 0.985  & 1.16~$\times10^{3}$ & 1.000 \\
                    \hline
                    64  & 1.50~$\times10^{4}$ & 0.378 & 1.78~$\times10^{3}$ & 0.677 & 3.32~$\times10^{0}$  & 1.000 & 2.61~$\times10^{1}$ & 0.968  & 1.10~$\times10^{3}$ & 1.000 \\
                    \hline
                    128 & 1.49~$\times10^{4}$ & 0.357 & 1.66~$\times10^{3}$ & 0.538 & 1.66~$\times10^{0}$  & 1.000 & 1.33~$\times10^{1}$ & 0.964  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                    256 & --                  & --    & 1.60~$\times10^{3}$ & 0.592 & 8.31~$\times10^{-1}$ & 1.000 & 6.65~$\times10^{0}$ & 0.962  & 1.06~$\times10^{3}$ & 1.000 \\
                    \hline
                    512 & --                  & --    & 1.83~$\times10^{3}$ & 0.581 & 4.16~$\times10^{-1}$ & 1.000 & 3.56~$\times10^{0}$ & 0.949  & 1.04~$\times10^{3}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{glove-25} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{table:results:ann-glove-25}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Multiplier}  & \multicolumn{2}{|c|}{\textbf{hnsw}} & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall     & QPS & Recall    \\
                    \hline
                    1   & 2.28~$\times10^{4}$ & 0.801 & 2.83~$\times10^{3}$ & 0.835 & 2.78~$\times10^{2}$ & 1.000 & 2.38~$\times10^{3}$ & 1.000* & 7.22~$\times10^{2}$ & 1.000* \\
                    \hline
                    2   & 2.38~$\times10^{4}$ & 0.607 & 2.70~$\times10^{3}$ & 0.832 & 1.39~$\times10^{2}$ & 1.000 & 1.19~$\times10^{3}$ & 1.000* & 5.75~$\times10^{2}$ & 1.000* \\
                    \hline
                    4   & 2.50~$\times10^{4}$ & 0.443 & 2.61~$\times10^{3}$ & 0.839 & 6.98~$\times10^{1}$ & 1.000 & 6.19~$\times10^{2}$ & 1.000* & 6.25~$\times10^{2}$ & 1.000* \\
                    \hline
                    8   & 2.78~$\times10^{4}$ & 0.294 & 2.51~$\times10^{3}$ & 0.834 & 3.49~$\times10^{1}$ & 1.000 & 3.03~$\times10^{2}$ & 1.000* & 5.93~$\times10^{2}$ & 1.000* \\
                    \hline
                    16  & 3.11~$\times10^{4}$ & 0.213 & 2.23~$\times10^{3}$ & 0.885 & 1.74~$\times10^{1}$ & 1.000 & 1.51~$\times10^{2}$ & 1.000* & 5.49~$\times10^{2}$ & 1.000* \\
                    \hline
                    32  & 3.24~$\times10^{4}$ & 0.178 & 2.01~$\times10^{3}$ & 0.764 & 8.70~$\times10^{0}$ & 1.000 & 7.40~$\times10^{1}$ & 0.999  & 4.75~$\times10^{2}$ & 1.000* \\
                    \hline
                    64  & --                  & --    & 1.99~$\times10^{3}$ & 0.631 & 4.36~$\times10^{0}$ & 1.000 & 3.77~$\times10^{1}$ & 0.997  & 4.61~$\times10^{2}$ & 1.000* \\
                    \hline
                    128 & --                  & --    & --                  & --    & 2.18~$\times10^{0}$ & 1.000 & 1.90~$\times10^{1}$ & 0.998  & 4.41~$\times10^{2}$ & 1.000* \\
                    \hline
                    256 & --                  & --    & --                  & --    & 1.07~$\times10^{0}$ & 1.000 & 9.47~$\times10^{0}$ & 0.998  & 4.23~$\times10^{2}$ & 1.000* \\
                    \hline
                    % 512 & -- & -- & -- & -- & 0.544 & 1.000 & 4.499 & 0.996 & 0.000 & 0.000 \\
                    % \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall on the \textbf{sift} dataset. 1.000* denotes imperfect recall that rounds to 1.000.}
    \label{table:results:ann-sift}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|p{1.2cm}|p{0.8cm}|}
                    \hline
                    \textbf{Multiplier}  & \multicolumn{2}{|c|}{\textbf{hnsw}}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall    & QPS & Recall    \\
                    \hline
                    1   & 1.93~$\times10^{4}$ & 0.782 & 3.98~$\times10^{3}$ & 0.686 & 7.26~$\times10^{1}$  & 1.000 & 6.98~$\times10^{2}$ & 1.000* & 5.52~$\times10^{2}$ & 1.000 \\
                    \hline
                    2   & 2.03~$\times10^{4}$ & 0.552 & 3.80~$\times10^{3}$ & 0.614 & 3.62~$\times10^{1}$  & 1.000 & 3.30~$\times10^{2}$ & 1.000* & 2.66~$\times10^{2}$ & 1.000 \\
                    \hline
                    4   & 2.18~$\times10^{4}$ & 0.394 & 3.69~$\times10^{3}$ & 0.637 & 1.82~$\times10^{1}$  & 1.000 & 1.65~$\times10^{2}$ & 1.000* & 1.43~$\times10^{2}$ & 1.000 \\
                    \hline
                    8   & 2.48~$\times10^{4}$ & 0.298 & 3.58~$\times10^{3}$ & 0.710 & 9.08~$\times10^{0}$  & 1.000 & 7.72~$\times10^{1}$ & 1.000* & 7.94~$\times10^{1}$ & 1.000 \\
                    \hline
                    16  & 2.68~$\times10^{4}$ & 0.210 & 3.50~$\times10^{3}$ & 0.690 & 4.54~$\times10^{0}$  & 1.000 & 3.98~$\times10^{1}$ & 1.000* & 8.12~$\times10^{1}$ & 1.000 \\
                    \hline
                    32  & 2.75~$\times10^{4}$ & 0.193 & 3.44~$\times10^{3}$ & 0.639 & 2.27~$\times10^{0}$  & 1.000 & 2.09~$\times10^{1}$ & 0.999  & 7.81~$\times10^{1}$ & 1.000 \\
                    \hline
                    64  & --                  & --    & 3.39~$\times10^{3}$ & 0.678 & 1.14~$\times10^{0}$  & 1.000 & 8.87~$\times10^{0}$ & 0.997  & 7.43~$\times10^{1}$ & 1.000 \\
                    \hline
                    128 & --                  & --    & 3.36~$\times10^{3}$ & 0.643 & 5.66~$\times10^{-1}$ & 1.000 & 4.78~$\times10^{0}$ & 0.993  & 6.80~$\times10^{1}$ & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}
